---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# synmort

<!-- badges: start -->
<!-- badges: end -->

Synthetic data on deaths and population in Australia.


## Installation

``` r
devtools::install_github("bayesiandemography/synmort")
```

## Description

**synmort** contains a single data frame
(called `synmort`) with synthetic data on deaths and population.
The data is based on a public domain dataset from the Australian Bureau of
Statistics. However, the original broad age groups have been split
into single-year age groups, and deaths have been randomly generated
from death rates and population counts. The data no longer accurately
reflects actual mortality patterns. It should be used
for developing code that that will ultimately be used on real data.

```{r}
library(synmort)
head(synmort)
```

